---
title: "How to use `nma` S3 methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-use-S3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This document describes how to use the main functions of `NMA` to run a network meta-analysis.

## Example

```{r setup, warning=FALSE, message=FALSE}
library(NMA)
library(dplyr)
library(purrr)
```

### Settings

Define the BUGS parameters for MCMC.

```{r}
bugs_params <-
  list(
    PROG = "openBugs",
    N.BURNIN = 10,#00,
    N.SIMS = 150,#0,
    N.CHAINS = 2,
    N.THIN = 1,
    PAUSE = TRUE)
```

Define the scenario we will use for the analysis.
We will load in a dataframe of values.

```{r}
analyses_params <-
  read.csv(
    here::here("raw_data", "AnalysisList.csv"),
    as.is = TRUE,
    na.strings = c("NR", "NA")) %>% 
  filter(Endpoint_type == "Surv") %>% 
  dplyr::rename(name = Analysis_name,
                type = Analysis_Type)

```

For demonstration purposes we will select the first scenario to run.

```{r}
analysis <- analyses_params[1, ]

# fixed effects RANDOM=FALSE, random effects RANDOM=TRUE
RANDOM <- analysis$Model_effects == "RE"

REFTX <- analysis$REFTX

# indicator for availability of binary endpoint data
is_bin <- analysis$BinData == "YES"

# indicator for availability of median endpoint data
is_med <- analysis$MedData == "YES"
```

### Read in datasets

The trials data consist of upto 3 separate dataframes.
A main table, `subData`, and optional tables for median event time and binary data, `subDataMed` and `subDataBin` respectively.

```{r}
file_name <- paste0(here::here("raw_data"), "/survdata_", analysis$Endpoint, "_")

subData <-
  read.csv(paste0(file_name, analysis$type, ".csv"),
           header = TRUE,
           as.is = TRUE)

subDataBin <-
  if (is_bin) {
    read.csv(paste0(file_name, "bin.csv"),
             header = TRUE,
             as.is = TRUE)
  } else {NA}

subDataMed <-
  if (is_med) {
    read.csv(paste0(file_name, "med.csv"),
             header = TRUE,
             as.is = TRUE) %>% 
      mutate(medR = floor(medR))
  } else {NA}
```


### Build model

Now we can create the NMA object to use in the modelling.

```{r}
nma_model <-
  new_NMA(subData = subData,
          subDataMed = subDataMed,
          subDataBin = subDataBin,
          bugs_params = bugs_params,
          is_random = RANDOM,
          refTx = REFTX ,
          effectParam = "beta",
          modelParams = "totresdev",
          label = analysis$name,
          endpoint = analysis$Endpoint)

nma_model
```

### Run MCMC

```{r}
nma_res <- NMA_run(nma_model)

nma_res

# diagnostics(nma_res)
# nma_outputs(nma_res)
```

### Reconfigure model

It is simple to modify an existing analysis without repeating the previous steps.
For example, we can run the NMA for a random effects model version of the same model.

```{r}
nma_model2 <-
  NMA_update(nma_model,
             is_random = TRUE)

nma_res2 <- NMA_run(nma_model2,
                    output_dir = "RE output")

# diagnostics(nma_res2, save = TRUE)
# nma_outputs(nma_res2, save = TRUE)

# plotNetwork(nma_model)

```
