---
title: "How to use `NMA`: Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-use-S3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This document describes how to use the main functions of `NMA` to run a single network meta-analysis.

## Example

```{r setup, warning=FALSE, message=FALSE}
library(NMA)
library(dplyr)
library(BRugs)
library(purrr)
```

### Settings

Define the BUGS parameters for MCMC.

```{r}
bugs_params <-
  list(
    PROG = "openBugs",
    N.BURNIN = 10,#00,
    N.SIMS = 150,#0,
    N.CHAINS = 2,
    N.THIN = 1,
    PAUSE = TRUE)
```

Define the scenario we will use for the analysis.

```{r eval=FALSE, echo=FALSE}
# We will load in a dataframe of values.
analyses_params <-
  read.csv(
    here::here("raw_data", "AnalysisList.csv"),
    as.is = TRUE,
    na.strings = c("NR", "NA")) %>% 
  filter(Endpoint_type == "Surv") %>% 
  dplyr::rename(name = Analysis_name,
                type = Analysis_Type)

```

```{r eval=FALSE, echo=FALSE}
# For demonstration purposes we will select the first scenario to run.
analysis <- analyses_params[1, ]

RANDOM <- analysis$Model_effects == "RE"  # fixed effects FALSE, random effects TRUE
is_bin <- analysis$BinData == "YES"       # indicator if binary endpoint data
is_med <- analysis$MedData == "YES"       # indicator if median endpoint data
REFTX <- analysis$REFTX                   # reference treatment
label_name <- analysis$name
endpoint <- analysis$Endpoint
analysis_type <- analysis$type
```

```{r}
RANDOM <- FALSE
REFTX <- "ERL/GEF"
is_bin <- TRUE
is_med <- TRUE
label_name <- "BC_PFS_mFE"
endpoint <- "PFS"
analysis_type <- "BC"
```


### Read in datasets

The trials data consist of up to 3 separate dataframes.
A main table, `subData`, and optional tables for median event time and binary data, `subDataMed` and `subDataBin` respectively.

```{r}
file_name <- paste0(here::here("raw_data"), "/survdata_", endpoint, "_")

subData <-
  read.csv(paste0(file_name, analysis_type, ".csv"),
           header = TRUE,
           as.is = TRUE)

subDataBin <-
  if (is_bin) {
    read.csv(paste0(file_name, "bin.csv"),
             header = TRUE,
             as.is = TRUE)
  } else {NA}

subDataMed <-
  if (is_med) {
    read.csv(paste0(file_name, "med.csv"),
             header = TRUE,
             as.is = TRUE) %>% 
      mutate(medR = floor(medR))
  } else {NA}
```


### Build model

Now we can create the NMA object to use in the modelling.

```{r}
nma_model <-
  new_NMA(subData = subData,
          subDataMed = subDataMed,
          subDataBin = subDataBin,
          bugs_params = bugs_params,
          is_random = RANDOM,
          refTx = REFTX ,
          effectParam = "beta",
          modelParams = "totresdev",
          label = label_name,
          endpoint = endpoint)

nma_model
```

We can view the network graph.

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=6}
library(sna)
plotNetwork(nma_model)
```


### Run MCMC

```{r}
nma_res <- NMA_run(nma_model)

nma_res

# diagnostics(nma_res)
# nma_outputs(nma_res)
```

### Reconfigure model

It is simple to modify an existing analysis without repeating the previous steps.
For example, we can run the NMA for a random effects model version of the same model.

```{r eval=FALSE}
##TODO: error 
# Error in scan(paste(tempDir, "/output", i, ".txt", sep = ""), switch(cmdtypes[i], : 
# scan() expected 'a real', got '1.#INF00'

nma_model2 <-
  NMA_update(nma_model,
             is_random = TRUE)

nma_res2 <- NMA_run(nma_model2,
                    output_dir = "RE output")

nma_res2

# diagnostics(nma_res2, save = TRUE)
# nma_outputs(nma_res2, save = TRUE)
```
