---
title: "Running an NMA with a Reference file and test data"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Running-an-NMA-with-a-Reference-file-and-test-data}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(NMA)
library(purrr)
```

Borrowing from the approach in the `heemod` package, as well as defining the analysis in an `R` script it is also possible to specify the analysis with only file inputs.
This vignette will show how to do this with a simple example.

## Introduction
The idea is to create folder with all of the information needed to run the NMA analysis contained in files within.
The meta information about the contents of the folder is contained in a _reference file_. The reference file is called `REFERENCE.csv`.

## Reference file
This file contains two columns called `type` and `file`.
Rows in the `type` column must contain one of the following keywords:

* `bugs`: File containing the BUGS input parameters for MCMC
* `analysis`: File containing the scenario information
* `subData`: Mandatory NMA data. Required column headings of `tx`, `base`, `study`, `Lmean`, `Lse`, `multi_arm`
* `subDataBin`: Optional binary data. Required column headings of `tx`, `base`, `study`, `BinN`, `BinR`
* `subDataMed`: Optional median time data. Required column headings of `tx`, `base`, `study`, `medN`, `medR`, `median`

`type` | `file`
-----|------
`bugs` | `bugs.csv`
`analysis` | `analysis.csv`
`subData` | `subData.csv`


## Parameter files

`bugs.csv` includes: OpenBUGS or WinBUGS option `PROG`, `N.BURNIN`, `N.SIMS`, `N.CHAINS`, `N.THIN`, `PAUSE.`
For example,
    
    PROG, openBugs
    N.BURNIN, 1000
    N.SIMS, 1500
    N.CHAINS, 2
    N.THIN, 1
    PAUSE, TRUE
    
and `analysis.csv` includes: whether a random effects model, `is_random`; the type of survival data, `data_type`the reference treatment, `REFTX`; `effectParam`, `label` and `endpoint`.
For example,

    is_random, FALSE
    data_type, hr_data
    refTx, X
    effectParam, beta
    label, my_label
    endpoint, my_endpoint
    
    
## Running an NMA

A single call sets-up the NMA represented by the contents of the folder.

```{r setup-model}
nma_model <- new_NMA_dir(data_dir = here::here("inst/analysis_folder_test"))
```


### Run MCMC

The NMA MCMC function calls the appropriate BUGS model in the usual way.

```{r run-model}
nma_res <- NMA_run(nma_model, save = FALSE)

nma_res
```

